Abstractions for Type-Level Programming

### 2022-04-21 ack.tex
ack.tex

I would also like to thank the other members of my thesis committee, Paolo Giarrusso, Richard Eisenberg, and Viktor Kuncak, for agreeing to review my dissertation and for taking part in the committee.

>>>>

I would also like to thank the other members of my thesis committee, Paolo Giarrusso, Richard Eisenberg, and Viktor Kuncak, for reviewing my dissertation and for providing valuable feedback for improvement.
